A seamless, client-centric programming model for type safe web applications

### 2014-06-19 paper.tex
Remove "the handshake is a simple operation" from server example section.
Make it more explicit that Conc is an IO monad.

The handshake is a simple operation; an \lstinline!MVar! is associated with the
connecting client's session identifier, and the pair is prepended to the
recipient list. Notice how the application's server state is passed in as the
function's argument.

@@

A solution is given in the \emph{poor man's concurrency
monad}\ \cite{concurrencymonad}. Making use of a continuation monad with
primitive operations for forking a computation and atomically lifting an IO
computation into the monad, it is possible to implement cooperative
multitasking on top of the non-concurrent JavaScript runtime. This monad
allows us to implement \lstinline!MVar!s as our blocking primitive, with the
same semantics as their regular Haskell counterpart.\ \cite{ffi}
This concurrency-enhanced monad is used as the basis of the \lstinline!Client!
monad.

>>>>

An \lstinline!MVar! is associated with the
connecting client's session identifier, and the pair is prepended to the
recipient list. Notice how the application's server state is passed in as the
function's argument.

@@

A solution is given in the \emph{poor man's concurrency
monad}\ \cite{concurrencymonad}. Making use of a continuation monad with
primitive operations for forking a computation and atomically lifting an IO
computation into the monad, it is possible to implement cooperative
multitasking on top of the non-concurrent JavaScript runtime. This monad
allows us to implement \lstinline!MVar!s as our blocking primitive, with the
same semantics as their regular Haskell counterpart.\ \cite{ffi}
This concurrency-enhanced IO monad is used as the basis of the
\lstinline!Client! monad.
